---
title: "Psych-DS Overview Analysis Report"
subtitle: "Participant Demographics & Study Summary"
author: "Brian Leonard"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    theme: cosmo
    highlight: tango
    code_folding: hide
    df_print: paged
  pdf_document:
    toc: true
params:
  study_name: "Your Study Name"
  data_directory: ""  # Will be set interactively
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.width = 10,
  fig.height = 6
)

# Load required libraries
library(tidyverse)
library(jsonlite)
library(janitor)
library(lubridate)
library(DT)
library(plotly)
library(viridis)
library(knitr)
library(kableExtra)
library(ggplot2)
library(patchwork)

# Set theme for all plots
theme_set(theme_minimal() + 
          theme(plot.title = element_text(face = "bold"),
                legend.position = "bottom"))

# Color palette
colors <- c("#2E7D32", "#1976D2", "#F57C00", "#7B1FA2", "#C62828", 
            "#00796B", "#5D4037", "#455A64", "#FF6F00", "#4527A0")
```

```{r setup-paths, include=FALSE}
# Flexible setup that works whether the Rmd is in root directory or analysis/ subdirectory
# This allows the workflow: Download data → Place Rmd in root OR analysis/ → Knit

# Start with current directory
current_dir <- getwd()

# Function to find the root directory containing the data
find_data_root <- function(start_dir) {
  # Check if data directory exists in current location
  if (dir.exists(file.path(start_dir, "data"))) {
    return(start_dir)
  }
  
  # Check if we're in analysis/ and data is one level up
  parent_dir <- dirname(start_dir)
  if (dir.exists(file.path(parent_dir, "data"))) {
    return(parent_dir)
  }
  
  # If neither location has data, return NULL
  return(NULL)
}

# Find the root directory
root_dir <- find_data_root(current_dir)

if (is.null(root_dir)) {
  stop(paste(
    "Could not locate the data directory.\n",
    "Please ensure this Rmd file is placed either:\n",
    "  • In the root directory (next to the data/ folder), OR\n",
    "  • In an analysis/ subdirectory within the root\n\n",
    "Current directory:", current_dir, "\n",
    "Expected data directory locations:\n",
    "  •", file.path(current_dir, "data"), "\n",
    "  •", file.path(dirname(current_dir), "data")
  ))
}

# Set up standard Psych-DS paths
paths <- list(
  root = root_dir,
  data = file.path(root_dir, "data"),
  overview = file.path(root_dir, "data", "overview"),
  demographic = file.path(root_dir, "data", "demographic"),
  analysis = file.path(root_dir, "analysis")  # Always create analysis in root
)

# Create analysis directory if it doesn't exist
dir.create(paths$analysis, showWarnings = FALSE, recursive = TRUE)

# Verify we're in the right place by checking for Psych-DS indicators
psych_ds_indicators <- c(
  file.exists(file.path(root_dir, "dataset_description.json")),
  dir.exists(paths$overview),
  dir.exists(paths$data),
  length(list.files(root_dir, pattern = "_data\\.csv$", recursive = TRUE)) > 0
)

if (!any(psych_ds_indicators)) {
  stop(paste(
    "This doesn't appear to be a Lookit/Psych-DS data directory.\n",
    "The root directory should contain:\n",
    "  • dataset_description.json file\n",
    "  • data/ subdirectory with overview/ folder\n",
    "  • CSV files with '_data.csv' in the name\n\n",
    "Found root directory:", root_dir, "\n",
    "Current working directory:", current_dir
  ))
}

# Verify overview directory exists
if (!dir.exists(paths$overview)) {
  stop(paste(
    "Overview directory not found at:", paths$overview, "\n",
    "Please ensure your Lookit data download is complete and unzipped properly."
  ))
}

# Report where we found everything
cat("✅ Lookit data directory detected\n")
cat(paste("📁 Root directory:", root_dir, "\n"))
cat(paste("📊 Overview data:", paths$overview, "\n"))
cat(paste("📈 Analysis directory:", paths$analysis, "\n"))

if (current_dir != root_dir) {
  cat(paste("📍 Running from:", basename(current_dir), "subdirectory\n"))
} else {
  cat("📍 Running from root directory\n")
}
```

# 📊 Lookit Data Analysis Report


**Instructions for Use:**

1. Download your study data from Lookit (it will be a zip file)

2. Unzip the data to create a folder with your study files

3. This file should already be downloaded in your `analysis` folder. If not, Save this Rmd file in **either location**:
   - **Root directory** (next to `dataset_description.json` and `data/` folder), OR
   - **Analysis subdirectory** (create an `analysis/` folder and place the Rmd there)
   
4. Click "Knit" to generate your analysis report

This analysis focuses on participant demographics and overall study statistics using the overview data files from your Lookit study. The script will automatically detect whether you're running from the root or analysis directory.

## Study Information

```{r load-metadata, results='asis'}
# Load global metadata
metadata_file <- file.path(paths$root, "dataset_description.json")
if (file.exists(metadata_file)) {
  global_metadata <- fromJSON(metadata_file, flatten = TRUE)
  
  # Create a nice summary table
  metadata_summary <- tibble(
    Field = c("Study Name", "Description", "Schema Version", "Date Created", "Total Variables"),
    Value = c(
      global_metadata$name %||% "Not specified",
      substr(global_metadata$description %||% "Not specified", 1, 200),
      global_metadata$schemaVersion %||% "Not specified",
      as.character(global_metadata$dateCreated %||% Sys.Date()),
      length(global_metadata$variableMeasured) %||% 0
    )
  )
  
  metadata_summary %>%
    kable(format = "html", escape = FALSE) %>%
    kable_styling(bootstrap_options = c("striped", "hover"), 
                  full_width = FALSE,
                  position = "left") %>%
    column_spec(1, bold = TRUE, width = "200px") %>%
    column_spec(2, width = "600px")
} else {
  cat("⚠️ No dataset_description.json found. Please ensure you have a valid Psych-DS dataset.")
}
```

# 🔍 Data Loading & Structure

```{r load-overview-data, results='hide'}
# Load overview files
overview_files <- list.files(paths$overview, pattern = "_data\\.csv$", full.names = TRUE)

if (length(overview_files) == 0) {
  stop("No overview data files found. Please check your data directory structure.")
}

# Load all overview data
overview_data <- map(overview_files, function(file) {
  read_csv(file, show_col_types = FALSE) %>% clean_names()
})
names(overview_data) <- basename(overview_files)

# Identify children and responses files
children_file <- overview_data[[which(str_detect(names(overview_data), "children"))]]
responses_file <- overview_data[[which(str_detect(names(overview_data), "responses"))]]

cat("✅ Loaded overview data files:\n")
for (i in seq_along(overview_data)) {
  cat(paste("  •", names(overview_data)[i], "-", nrow(overview_data[[i]]), "rows\n"))
}
```

## Data Summary Statistics

```{r data-summary}
# Calculate summary statistics from overview data
if (!is.null(children_file) && !is.null(responses_file)) {
  summary_stats <- list(
    "Total Children" = nrow(children_file),
    "Total Responses" = nrow(responses_file),
    "Completed Responses" = sum(responses_file$response_completed == TRUE, na.rm = TRUE),
    "Unique Participants" = n_distinct(responses_file$participant_hashed_id),
    "Preview Responses" = sum(responses_file$response_is_preview == TRUE, na.rm = TRUE),
    "Withdrawn Responses" = sum(responses_file$response_withdrawn == TRUE, na.rm = TRUE)
  )
} else if (!is.null(responses_file)) {
  summary_stats <- list(
    "Total Responses" = nrow(responses_file),
    "Completed Responses" = sum(responses_file$response_completed == TRUE, na.rm = TRUE),
    "Unique Participants" = n_distinct(responses_file$participant_hashed_id),
    "Preview Responses" = sum(responses_file$response_is_preview == TRUE, na.rm = TRUE),
    "Withdrawn Responses" = sum(responses_file$response_withdrawn == TRUE, na.rm = TRUE),
    "Data Files Processed" = length(overview_files)
  )
} else {
  summary_stats <- list(
    "Data Files Found" = length(overview_files),
    "Total Rows" = sum(map_dbl(overview_data, nrow))
  )
}

# Create summary display
summary_df <- tibble(
  Metric = names(summary_stats),
  Value = as.character(summary_stats)
)

summary_df %>%
  kable(format = "html", col.names = NULL) %>%
  kable_styling(bootstrap_options = c("striped"), full_width = FALSE) %>%
  column_spec(1, bold = TRUE, color = "white", background = "#1976D2") %>%
  column_spec(2, bold = TRUE, background = "#E3F2FD")
```

# 👥 Participant Demographics

## Age Distribution

```{r age-analysis, fig.height=8}
# Find age data in overview files
age_data <- NULL

# First try children file
if (!is.null(children_file)) {
  age_data <- children_file
  data_source <- "children file"
} else if (!is.null(responses_file)) {
  age_data <- responses_file
  data_source <- "responses file"
}

if (!is.null(age_data) && nrow(age_data) > 0) {
  
  # First, check what age columns we actually have
  age_columns <- names(age_data)[str_detect(names(age_data), "age|birth")]
  cat("📋 Available age-related columns:", paste(age_columns, collapse = ", "), "\n\n")
  
  # Process age data - look for various age columns that actually exist
  age_processed <- age_data
  
  # Initialize age columns
  age_processed$age_days <- NA_real_
  age_processed$age_months <- NA_real_
  age_processed$age_years <- NA_real_
  
  # Try different age column patterns
  if ("child_age_in_days" %in% names(age_data)) {
    age_processed$age_days <- as.numeric(age_processed$child_age_in_days)
    age_processed$age_months <- age_processed$age_days / 30.44
    cat("✅ Using child_age_in_days column\n")
  } else if ("child_age_rounded" %in% names(age_data)) {
    # child_age_rounded is typically in days
    age_processed$age_days <- as.numeric(age_processed$child_age_rounded)
    age_processed$age_months <- age_processed$age_days / 30.44
    cat("✅ Using child_age_rounded column (assuming days)\n")
  } else {
    cat("⚠️ No recognized age columns found\n")
  }
  
  # Calculate age years and groups with smart bucketing
  age_processed <- age_processed %>%
    mutate(
      age_years = age_months / 12,
      # Smart age grouping: 3-month buckets up to 24 months, then yearly
      age_group = case_when(
        is.na(age_months) ~ "Unknown",
        age_months < 3 ~ "0-2 months",
        age_months < 6 ~ "3-5 months", 
        age_months < 9 ~ "6-8 months",
        age_months < 12 ~ "9-11 months",
        age_months < 15 ~ "12-14 months",
        age_months < 18 ~ "15-17 months",
        age_months < 21 ~ "18-20 months",
        age_months < 24 ~ "21-23 months",
        age_months < 36 ~ "2 years",
        age_months < 48 ~ "3 years",
        age_months < 60 ~ "4 years",
        age_months < 72 ~ "5 years",
        age_months < 84 ~ "6 years",
        age_months < 96 ~ "7 years",
        age_months < 108 ~ "8 years",
        age_months < 120 ~ "9 years",
        TRUE ~ "10+ years"
      )
    ) %>%
    filter(!is.na(age_months) & age_months > 0 & age_months < 240)
  
  # Create adaptive age groups based on actual data distribution
  if (nrow(age_processed) > 0) {
    min_age <- min(age_processed$age_months)
    max_age <- max(age_processed$age_months)
    age_range <- max_age - min_age
    
    # For very narrow age ranges (< 6 months), create meaningful sub-month groups
    if (age_range < 6) {
      # Create groups based on weeks/half-months for very narrow studies
      age_processed <- age_processed %>%
        mutate(
          adaptive_age_group = case_when(
            age_months < min_age + 0.5 ~ paste0(floor(min_age), ".0-", floor(min_age), ".5 months"),
            age_months < min_age + 1.0 ~ paste0(floor(min_age), ".5-", floor(min_age + 1), ".0 months"),
            age_months < min_age + 1.5 ~ paste0(floor(min_age + 1), ".0-", floor(min_age + 1), ".5 months"),
            age_months < min_age + 2.0 ~ paste0(floor(min_age + 1), ".5-", floor(min_age + 2), ".0 months"),
            age_months < min_age + 2.5 ~ paste0(floor(min_age + 2), ".0-", floor(min_age + 2), ".5 months"),
            TRUE ~ paste0(floor(min_age + 2), ".5-", ceiling(max_age), ".0 months")
          )
        )
    } else if (age_range < 12) {
      # For narrow ranges, use 2-month groups
      age_processed <- age_processed %>%
        mutate(
          adaptive_age_group = case_when(
            age_months < ceiling(min_age/2)*2 + 2 ~ paste0(floor(min_age), "-", ceiling(min_age/2)*2 + 1, " months"),
            age_months < ceiling(min_age/2)*2 + 4 ~ paste0(ceiling(min_age/2)*2 + 2, "-", ceiling(min_age/2)*2 + 3, " months"), 
            age_months < ceiling(min_age/2)*2 + 6 ~ paste0(ceiling(min_age/2)*2 + 4, "-", ceiling(min_age/2)*2 + 5, " months"),
            TRUE ~ paste0(ceiling(min_age/2)*2 + 6, "-", ceiling(max_age), " months")
          )
        )
    } else {
      # Use the standard smart grouping for wider ranges
      age_processed$adaptive_age_group <- age_processed$age_group
    }
  }
  
  if (nrow(age_processed) > 0) {
    # Calculate detailed statistics
    cat("📊 Age Distribution Statistics:\n")
    cat(paste("  • Data source:", data_source, "\n"))
    cat(paste("  • Sample size:", nrow(age_processed), "children\n"))
    cat(paste("  • Mean age:", round(mean(age_processed$age_months, na.rm = TRUE), 1), "months (", 
              round(mean(age_processed$age_years, na.rm = TRUE), 2), "years)\n"))
    cat(paste("  • Median age:", round(median(age_processed$age_months, na.rm = TRUE), 1), "months\n"))
    cat(paste("  • Age range:", round(min_age, 1), "-", round(max_age, 1), "months\n"))
    cat(paste("  • Standard deviation:", round(sd(age_processed$age_months, na.rm = TRUE), 1), "months\n"))
    cat(paste("  • Age span covered:", round(age_range, 1), "months\n"))
    
    
    cat("\n")
    
    # Age distribution histogram with better binning
    # Calculate optimal bin width based on data range
    age_range <- max(age_processed$age_months) - min(age_processed$age_months)
    bin_width <- case_when(
      age_range < 2 ~ 0.2,     # Very narrow: 0.2 month bins (about 6 days)
      age_range < 6 ~ 0.5,     # Narrow: 0.5 month bins (about 2 weeks)  
      age_range < 12 ~ 1,      # Moderate: 1 month bins
      age_range < 36 ~ 3,      # Wide: 3 month bins
      TRUE ~ 6                 # Very wide: 6 month bins
    )
    
    # Set reasonable axis breaks
    if (age_range < 6) {
      x_breaks <- seq(floor(min(age_processed$age_months)), 
                      ceiling(max(age_processed$age_months)), by = 0.5)
    } else if (age_range < 24) {
      x_breaks <- seq(floor(min(age_processed$age_months)), 
                      ceiling(max(age_processed$age_months)), by = 3)
    } else {
      x_breaks <- seq(floor(min(age_processed$age_months)), 
                      ceiling(max(age_processed$age_months)), by = 12)
    }
    
    p1 <- ggplot(age_processed, aes(x = age_months)) +
      geom_histogram(binwidth = bin_width, fill = colors[3], alpha = 0.8, color = "white") +
      geom_vline(aes(xintercept = mean(age_months, na.rm = TRUE)), 
                 color = "red", linetype = "dashed", size = 1) +
      geom_vline(aes(xintercept = median(age_months, na.rm = TRUE)), 
                 color = "blue", linetype = "dashed", size = 1) +
      labs(title = "Age Distribution of Participants",
           subtitle = paste("Red line = mean, Blue line = median | Bin width:", bin_width, "months"),
           x = "Age (months)",
           y = "Number of Children") +
      scale_x_continuous(breaks = x_breaks) +
      theme_minimal() +
      theme(
        plot.margin = margin(20, 20, 20, 20),
        axis.text.x = element_text(angle = 0, hjust = 0.5, size = 10)
      )
    
    # Age groups bar chart - ordered by age, not count
    age_group_summary <- age_processed %>%
      count(adaptive_age_group) %>%
      mutate(percentage = n / sum(n) * 100)
    
    # Create ordered factor based on age progression
    age_order <- c("0-2 months", "3-5 months", "6-8 months", "9-11 months", 
                   "12-14 months", "15-17 months", "18-20 months", "21-23 months",
                   "2 years", "3 years", "4 years", "5 years", "6 years", 
                   "7 years", "8 years", "9 years", "10+ years")
    
    # Filter to only include age groups that exist in the data and preserve order
    existing_age_groups <- intersect(age_order, age_group_summary$adaptive_age_group)
    
    # Add any age groups not in our predefined order (for adaptive grouping) at the end
    additional_groups <- setdiff(age_group_summary$adaptive_age_group, age_order)
    final_age_order <- c(existing_age_groups, sort(additional_groups))
    
    age_group_summary$adaptive_age_group <- factor(age_group_summary$adaptive_age_group, 
                                                   levels = final_age_order)
    
    p2 <- ggplot(age_group_summary, aes(x = adaptive_age_group, y = n, fill = adaptive_age_group)) +
      geom_col(alpha = 0.8) +
      geom_text(aes(label = paste0(n, "\n(", round(percentage, 1), "%)")), 
                hjust = -0.1, size = 3) +
      coord_flip() +
      scale_fill_viridis_d() +
      labs(title = "Participants by Age Group",
           subtitle = paste("Ordered by age progression | Study range:", 
                           round(min_age, 1), "-", round(max_age, 1), "months"),
           x = "Age Group",
           y = "Number of Children") +
      theme_minimal() +
      theme(
        legend.position = "none",
        plot.margin = margin(20, 20, 20, 20)
      ) +
      expand_limits(y = max(age_group_summary$n) * 1.15)
    
    
    # Display plots with full width
    print(p1)  # Histogram full width
    print(p2)  # Age groups full width  
    # Age by Gender Cross-tabulation
    if ("child_gender" %in% names(age_processed)) {
      # Create cross-tabulation data
      age_gender_crosstab <- age_processed %>%
        mutate(
          gender_label = case_when(
            child_gender == "f" ~ "Female",
            child_gender == "m" ~ "Male", 
            child_gender == "o" ~ "Other",
            child_gender == "na" ~ "Not specified",
            TRUE ~ as.character(child_gender)
          )
        ) %>%
        count(adaptive_age_group, gender_label) %>%
        pivot_wider(names_from = gender_label, values_from = n, values_fill = 0) %>%
        arrange(adaptive_age_group)
      
      # Add row totals
      if (ncol(age_gender_crosstab) > 1) {
        age_gender_crosstab <- age_gender_crosstab %>%
          rowwise() %>%
          mutate(Total = sum(c_across(-adaptive_age_group), na.rm = TRUE)) %>%
          ungroup()
        
        # Add column totals
        totals_row <- age_gender_crosstab %>%
          summarise(
            adaptive_age_group = "Total",
            across(-adaptive_age_group, sum, na.rm = TRUE)
          )
        
        age_gender_crosstab <- bind_rows(age_gender_crosstab, totals_row)
        
        # Create interactive table
        datatable(age_gender_crosstab,
                  options = list(
                    pageLength = 20,
                    scrollX = TRUE,
                    dom = 'Bfrtip',
                    buttons = c('copy', 'csv', 'excel')
                  ),
                  caption = "Participant Count by Age Group and Gender",
                  colnames = c("Age Group" = "adaptive_age_group")) %>%
          formatStyle(
            "Total",
            backgroundColor = "#e3f2fd",
            fontWeight = "bold"
          ) %>%
          formatStyle(
            1:nrow(age_gender_crosstab),
            target = "row",
            backgroundColor = styleEqual("Total", "#f5f5f5")
          )
      }
    } else {
      cat("ℹ️ Gender data not available for cross-tabulation with age groups.\n")
    }
  }
} else {
  cat("ℹ️ No age data found in overview files.\n")
}
```

## Gender Distribution

```{r gender-analysis}
if (!is.null(age_data) && "child_gender" %in% names(age_data)) {
  gender_summary <- age_data %>%
    filter(!is.na(child_gender)) %>%
    count(child_gender) %>%
    mutate(
      percentage = n / sum(n) * 100,
      gender_label = case_when(
        child_gender == "f" ~ "Female",
        child_gender == "m" ~ "Male",
        child_gender == "o" ~ "Other",
        child_gender == "na" ~ "Prefer not to answer",
        TRUE ~ as.character(child_gender)
      )
    )
  
  # Create pie chart - full width
  plot_ly(gender_summary, 
          labels = ~gender_label, 
          values = ~n,
          type = 'pie',
          textposition = 'inside',
          textinfo = 'label+percent',
          marker = list(colors = colors[1:nrow(gender_summary)]),
          hovertemplate = "%{label}<br>Count: %{value}<br>Percentage: %{percent}<extra></extra>",
          width = 1000, height = 500) %>%
    layout(title = list(text = "Gender Distribution<br><sub>Parent-reported gender identity</sub>"),
           showlegend = TRUE,
           margin = list(l = 50, r = 50, t = 100, b = 50))
} else {
  cat("ℹ️ No gender data found in overview files.\n")
}
```

## Language Information

```{r language-analysis}
if (!is.null(age_data) && "child_language_list" %in% names(age_data)) {
  # Process language data - keep combinations together
  language_data <- age_data %>%
    filter(!is.na(child_language_list) & child_language_list != "") %>%
    mutate(
      # Clean up language combinations and sort languages within each combination
      language_combination = map_chr(child_language_list, function(lang_string) {
        # Split, sort, and rejoin to standardize order (e.g., "es en" becomes "en es")
        langs <- str_split(lang_string, " ")[[1]]
        langs <- langs[langs != ""]  # Remove empty strings
        paste(sort(langs), collapse = " ")
      })
    ) %>%
    count(language_combination, sort = TRUE) %>%
    head(15)  # Top 15 language combinations
  
  if (nrow(language_data) > 0) {
    # Create bar chart - full width
    ggplot(language_data, aes(x = reorder(language_combination, n), y = n)) +
      geom_col(fill = colors[4], alpha = 0.8) +
      geom_text(aes(label = n), hjust = -0.1, size = 3.5) +
      coord_flip() +
      labs(title = "Language Combinations Spoken by Participants",
           subtitle = "Top 15 most common language combinations",
           x = "Language Combination",
           y = "Number of Children") +
      theme_minimal() +
      theme(plot.margin = margin(20, 20, 20, 20)) +
      expand_limits(y = max(language_data$n) * 1.15)
  }
} else {
  cat("ℹ️ No language data found in overview files.\n")
}
```

# 📈 Response Analysis

## Response Completion Status

```{r response-completion}
if (!is.null(responses_file)) {
  # Check which response columns exist
  response_cols <- names(responses_file)
  
  # Response completion analysis - handle missing columns gracefully
  completion_summary <- responses_file %>%
    summarise(
      total_responses = n(),
      completed = ifelse("response_completed" %in% names(responses_file), 
                        sum(response_completed == TRUE, na.rm = TRUE), 0),
      incomplete = ifelse("response_completed" %in% names(responses_file),
                         sum(response_completed == FALSE, na.rm = TRUE), 0),
      preview = ifelse("response_is_preview" %in% names(responses_file),
                      sum(response_is_preview == TRUE, na.rm = TRUE), 0),
      withdrawn = ifelse("response_withdrawn" %in% names(responses_file),
                        sum(response_withdrawn == TRUE, na.rm = TRUE), 0)
    ) %>%
    mutate(
      completion_rate = ifelse(completed + incomplete > 0, 
                              round(completed / (completed + incomplete) * 100, 1), 
                              NA_real_)
    )
  
  # Create completion status visualization only for available columns
  status_data <- tibble(
    Status = character(),
    Count = numeric(),
    Percentage = numeric()
  )
  
  if ("response_completed" %in% names(responses_file)) {
    status_data <- bind_rows(status_data,
      tibble(Status = c("Completed", "Incomplete"),
             Count = c(completion_summary$completed, completion_summary$incomplete)))
  }
  
  if ("response_is_preview" %in% names(responses_file) && completion_summary$preview > 0) {
    status_data <- bind_rows(status_data,
      tibble(Status = "Preview", Count = completion_summary$preview))
  }
  
  if ("response_withdrawn" %in% names(responses_file) && completion_summary$withdrawn > 0) {
    status_data <- bind_rows(status_data,
      tibble(Status = "Withdrawn", Count = completion_summary$withdrawn))
  }
  
  if (nrow(status_data) > 0) {
    status_data <- status_data %>%
      mutate(Percentage = round(Count / completion_summary$total_responses * 100, 1))
    
    plot_ly(status_data, 
            x = ~Status, 
            y = ~Count, 
            type = 'bar',
            marker = list(color = colors[1:nrow(status_data)]),
            text = ~paste("Count:", Count, "<br>Percentage:", Percentage, "%"),
            hovertemplate = "%{x}<br>%{text}<extra></extra>",
            width = 1000, height = 500) %>%
      layout(title = list(text = ifelse(!is.na(completion_summary$completion_rate),
                                       paste("Response Completion Status<br><sub>Overall completion rate:", 
                                           completion_summary$completion_rate, "%</sub>"),
                                       "Response Status Overview")),
             xaxis = list(title = "Response Status"),
             yaxis = list(title = "Number of Responses"),
             margin = list(l = 50, r = 50, t = 100, b = 50))
  }
  
  # Summary statistics table
  cat("\n📊 Response Summary:\n")
  cat(paste("  • Total responses:", completion_summary$total_responses, "\n"))
  if ("response_completed" %in% names(responses_file)) {
    cat(paste("  • Completed responses:", completion_summary$completed, "\n"))
    if (!is.na(completion_summary$completion_rate)) {
      cat(paste("  • Completion rate:", completion_summary$completion_rate, "%\n"))
    }
  }
  if ("response_is_preview" %in% names(responses_file)) {
    cat(paste("  • Preview responses:", completion_summary$preview, "\n"))
  }
  if ("response_withdrawn" %in% names(responses_file)) {
    cat(paste("  • Withdrawn responses:", completion_summary$withdrawn, "\n"))
  }
}
```

# 📊 JSON Data Loading (Optimized)

```{r load-json-data, include=FALSE}
# Load JSON data once and process efficiently
json_file <- file.path(paths$data, "raw", "all_responses_identifiable.json")
all_responses_data <- NULL
json_processing_time <- NULL

if (file.exists(json_file)) {
  cat("📁 Loading detailed response data...\n")
  start_time <- Sys.time()
  
  # Load JSON data once
  all_responses_data <- fromJSON(json_file, flatten = TRUE)
  
  # Pre-process all the data we need in vectorized operations
  if (!is.null(all_responses_data) && nrow(all_responses_data) > 0) {
    
    # Filter out preview responses once
    non_preview_mask <- !all_responses_data$response.is_preview
    
    # Extract basic info
    response_info <- tibble(
      response_uuid = all_responses_data$response.uuid[non_preview_mask],
      completed = all_responses_data$response.completed[non_preview_mask],
      is_preview = all_responses_data$response.is_preview[non_preview_mask]
    )
    
    # Process sequences efficiently
    sequences_list <- all_responses_data$response.sequence[non_preview_mask]
    sequence_info <- map_dfr(seq_along(sequences_list), function(i) {
      seq_data <- sequences_list[[i]]
      if (!is.null(seq_data) && length(seq_data) > 0) {
        tibble(
          response_uuid = response_info$response_uuid[i],
          total_frames = length(seq_data),
          last_frame = seq_data[length(seq_data)],
          sequence_preview = if(length(seq_data) > 3) {
            paste(c(seq_data[1:3], "..."), collapse = " → ")
          } else {
            paste(seq_data, collapse = " → ")
          }
        )
      } else {
        tibble(
          response_uuid = response_info$response_uuid[i],
          total_frames = 0,
          last_frame = "No sequence data",
          sequence_preview = "No sequence data"
        )
      }
    })
    
    # Process conditions efficiently
    conditions_list <- all_responses_data$response.conditions[non_preview_mask]
    condition_info <- map_dfr(seq_along(conditions_list), function(i) {
      cond_data <- conditions_list[[i]]
      if (!is.null(cond_data) && length(cond_data) > 0) {
        # Handle different condition data structures
        if (is.data.frame(cond_data)) {
          condition_df <- cond_data
        } else if (is.list(cond_data)) {
          condition_df <- bind_rows(cond_data)
        } else {
          return(tibble(
            response_uuid = response_info$response_uuid[i],
            frame_name = "No conditions",
            condition_num = NA_real_
          ))
        }
        
        if (nrow(condition_df) > 0) {
          return(tibble(
            response_uuid = response_info$response_uuid[i],
            frame_name = condition_df$frameName,
            condition_num = condition_df$conditionNum
          ))
        }
      }
      
      return(tibble(
        response_uuid = response_info$response_uuid[i],
        frame_name = "No conditions",
        condition_num = NA_real_
      ))
    })
    
    # Store processed data globally for reuse
    processed_json_data <- list(
      response_info = response_info,
      sequence_info = sequence_info,
      condition_info = condition_info
    )
    
    end_time <- Sys.time()
    json_processing_time <- round(as.numeric(difftime(end_time, start_time, units = "secs")), 2)
    
    cat("✅ JSON data processed in", json_processing_time, "seconds\n")
    cat("📊 Processed", nrow(response_info), "non-preview responses\n")
    
  } else {
    cat("⚠️ JSON file found but could not be processed\n")
  }
} else {
  cat("ℹ️ all_responses_identifiable.json not found - some analyses will be limited\n")
}
```

## Incomplete Response Analysis

```{r incomplete-responses}
if (!is.null(responses_file) && "response_completed" %in% names(responses_file)) {
  # Find incomplete responses
  incomplete_responses <- responses_file %>%
    filter(
      response_is_preview == FALSE,
      response_completed == FALSE
    )
  
  if (nrow(incomplete_responses) > 0) {
    cat("📊 Incomplete Response Summary:\n")
    cat(paste("  • Total incomplete responses:", nrow(incomplete_responses), "\n"))
    cat(paste("  • Completion rate:", 
              round(mean(responses_file$response_completed == TRUE, na.rm = TRUE) * 100, 1), 
              "%\n\n"))
    
    # Use pre-processed JSON data if available
    if (exists("processed_json_data") && !is.null(processed_json_data)) {
      cat("📁 Using pre-processed sequence data for dropout analysis\n\n")
      
      # Filter sequence data for incomplete responses only
      incomplete_sequence_data <- processed_json_data$sequence_info %>%
        filter(response_uuid %in% incomplete_responses$response_uuid)
      
      # Merge with incomplete responses data
      incomplete_summary <- incomplete_responses %>%
        left_join(incomplete_sequence_data, by = "response_uuid") %>%
        select(response_uuid, child_hashed_id, total_frames, last_frame, sequence_preview,
               any_of(c("response_date_created", "consent_ruling"))) %>%
        arrange(desc(total_frames))
      
      # Display summary statistics
      if (any(!is.na(incomplete_summary$total_frames) & incomplete_summary$total_frames > 0)) {
        valid_frames <- incomplete_summary$total_frames[!is.na(incomplete_summary$total_frames) & incomplete_summary$total_frames > 0]
        
        cat("📊 Dropout Analysis Results:\n")
        cat(paste("  • Responses with sequence data:", length(valid_frames), "of", nrow(incomplete_responses), "\n"))
        cat(paste("  • Average frames completed before dropout:", round(mean(valid_frames), 1), "\n"))
        cat(paste("  • Median frames completed:", round(median(valid_frames), 1), "\n"))
        cat(paste("  • Range of frames completed:", min(valid_frames), "-", max(valid_frames), "\n"))
        
        # Find most common dropout points
        dropout_frames <- incomplete_summary$last_frame[incomplete_summary$last_frame != "No sequence data" & 
                                                       incomplete_summary$last_frame != "No frames"]
        if (length(dropout_frames) > 0) {
          common_dropouts <- table(dropout_frames) %>% 
            sort(decreasing = TRUE) %>% 
            head(5)
          
          cat("\n🎯 Most common dropout points:\n")
          for (i in 1:length(common_dropouts)) {
            cat(paste("  •", names(common_dropouts)[i], ":", common_dropouts[i], "participants\n"))
          }
        }
        cat("\n")
      }
      
      # Create interactive table
      datatable(incomplete_summary,
                options = list(
                  pageLength = 15,
                  scrollX = TRUE,
                  dom = 'Bfrtip',
                  buttons = c('copy', 'csv', 'excel'),
                  columnDefs = list(
                    list(width = '200px', targets = c(0, 1)),
                    list(width = '100px', targets = 2),
                    list(width = '150px', targets = 3),
                    list(width = '300px', targets = 4)
                  )
                ),
                filter = 'top',
                caption = "Incomplete Responses with Sequence Analysis",
                colnames = c(
                  "Response UUID" = "response_uuid",
                  "Child Hashed ID" = "child_hashed_id",
                  "Frames Completed" = "total_frames",
                  "Last Frame" = "last_frame",
                  "Sequence Preview" = "sequence_preview",
                  "Date Created" = "response_date_created",
                  "Consent" = "consent_ruling"
                )) %>%
        formatStyle(
          "Frames Completed",
          backgroundColor = styleInterval(c(5, 15, 30), 
                                        c("#ffcdd2", "#ffecb3", "#fff3e0", "#e8f5e8")),
          fontWeight = "bold"
        )
      
    } else {
      cat("⚠️ No pre-processed JSON data available\n")
      cat("   Using basic incomplete response information instead\n\n")
      
      # Fallback: Just show incomplete responses without sequence analysis  
      incomplete_summary <- incomplete_responses %>%
        select(response_uuid, child_hashed_id, 
               any_of(c("response_date_created", "consent_ruling", "response_eligibility_0")))
      
      datatable(incomplete_summary,
                options = list(
                  pageLength = 15,
                  scrollX = TRUE,
                  dom = 'Bfrtip',
                  buttons = c('copy', 'csv', 'excel')
                ),
                filter = 'top',
                caption = "Incomplete Responses",
                colnames = c(
                  "Response UUID" = "response_uuid",
                  "Child Hashed ID" = "child_hashed_id",
                  "Date Created" = "response_date_created",
                  "Consent" = "consent_ruling"
                ))
    }
    
  } else {
    cat("✅ All responses were completed successfully!\n")
  }
} else {
  cat("ℹ️ No completion status information available.\n")
}
```

## Condition Assignment Distribution

```{r condition-analysis}
# Use pre-processed JSON data if available
if (exists("processed_json_data") && !is.null(processed_json_data)) {
  cat("📊 Analyzing experimental conditions from pre-processed data...\n\n")
  
  # Use pre-processed condition data
  condition_data <- processed_json_data$condition_info
  
  if (nrow(condition_data) > 0) {
    # Summary statistics
    total_responses <- n_distinct(condition_data$response_uuid)
    responses_with_conditions <- sum(!is.na(condition_data$condition_num))
    unique_frames <- n_distinct(condition_data$frame_name[!is.na(condition_data$condition_num)])
    unique_conditions <- n_distinct(condition_data$condition_num[!is.na(condition_data$condition_num)])
    
    cat("📋 Condition Assignment Summary:\n")
    cat(paste("  • Total responses analyzed:", total_responses, "\n"))
    cat(paste("  • Responses with conditions:", responses_with_conditions, "\n"))
    cat(paste("  • Unique randomization frames:", unique_frames, "\n"))
    cat(paste("  • Unique condition numbers:", unique_conditions, "\n\n"))
    
    # Condition distribution analysis
    if (responses_with_conditions > 0) {
      # Overall condition distribution
      condition_summary <- condition_data %>%
        filter(!is.na(condition_num)) %>%
        count(condition_num) %>%
        mutate(
          percentage = round(n / sum(n) * 100, 1),
          condition_label = paste0("Condition ", condition_num)
        ) %>%
        arrange(condition_num)
      
      # Create bar chart
      if (nrow(condition_summary) > 0) {
        p_conditions <- ggplot(condition_summary, aes(x = factor(condition_num), y = n, fill = condition_label)) +
          geom_col(alpha = 0.8) +
          geom_text(aes(label = paste0(n, "\n(", percentage, "%)")), 
                    vjust = -0.5, size = 3.5) +
          scale_fill_viridis_d(option = "turbo") +
          labs(title = "Distribution of Experimental Conditions",
               subtitle = paste("Randomization across", unique_conditions, "conditions |", 
                               responses_with_conditions, "participants assigned"),
               x = "Condition Number",
               y = "Number of Participants") +
          theme_minimal() +
          theme(
            legend.position = "none",
            plot.margin = margin(20, 20, 20, 20)
          ) +
          expand_limits(y = max(condition_summary$n) * 1.15)
        
        print(p_conditions)
      }
      
      
    } else {
      cat("ℹ️ No condition assignments found in the data\n")
    }
    
  } else {
    cat("ℹ️ No condition data could be extracted from responses\n")
  }
  
} else {
  cat("ℹ️ No pre-processed JSON data available for condition analysis\n")
}
```

## Response Timeline

```{r response-timeline}
if (!is.null(responses_file) && "response_date_created" %in% names(responses_file)) {
  # Process dates
  timeline_data <- responses_file %>%
    mutate(
      date = as.Date(response_date_created),
      week = floor_date(date, "week"),
      month = floor_date(date, "month")
    ) %>%
    filter(!is.na(date))
  
  # Filter out preview responses if that column exists
  if ("response_is_preview" %in% names(timeline_data)) {
    timeline_data <- timeline_data %>% filter(response_is_preview == FALSE)
  }
  
  if (nrow(timeline_data) > 0) {
    # Overall responses over time
    weekly_responses <- timeline_data %>%
      count(week) %>%
      arrange(week)
    
    p_timeline <- ggplot(weekly_responses, aes(x = week, y = n)) +
      geom_line(color = colors[2], size = 1.2) +
      geom_point(color = colors[2], size = 3) +
      labs(title = "Response Collection Timeline",
           subtitle = "Number of responses per week",
           x = "Date",
           y = "Number of Responses") +
      theme_minimal() +
      theme(
        axis.text.x = element_text(angle = 45, hjust = 1),
        plot.margin = margin(20, 20, 20, 20)
      ) +
      scale_x_date(date_labels = "%Y-%m-%d", date_breaks = "1 week")
    
    # Age-stratified timeline (if we have age data)
    if (exists("age_processed") && nrow(age_processed) > 0) {
      # Merge timeline data with age groups
      timeline_with_age <- timeline_data %>%
        left_join(
          age_processed %>% select(child_hashed_id, adaptive_age_group),
          by = "child_hashed_id"
        ) %>%
        filter(!is.na(adaptive_age_group))
      
      if (nrow(timeline_with_age) > 0) {
        # Create complete date sequence for all weeks
        all_weeks <- seq(min(timeline_data$week), max(timeline_data$week), by = "week")
        all_age_groups <- unique(timeline_with_age$adaptive_age_group)
        
        # Create complete grid of all week-age combinations
        complete_grid <- expand_grid(
          week = all_weeks,
          adaptive_age_group = all_age_groups
        )
        
        # Weekly responses by age group - with zeros for missing combinations
        weekly_by_age <- timeline_with_age %>%
          count(week, adaptive_age_group) %>%
          right_join(complete_grid, by = c("week", "adaptive_age_group")) %>%
          mutate(n = replace_na(n, 0)) %>%
          arrange(week, adaptive_age_group)
        
        # Create age-stratified timeline with continuous lines
        p_timeline_age <- ggplot(weekly_by_age, aes(x = week, y = n, color = adaptive_age_group)) +
          geom_line(size = 1.2) +
          geom_point(size = 2.5) +
          scale_color_viridis_d(option = "turbo", name = "Age Group") +
          labs(title = "Response Collection Timeline by Age Group",
               subtitle = "Separate lines for each age group - helps identify recruitment patterns",
               x = "Date",
               y = "Number of Responses") +
          theme_minimal() +
          theme(
            axis.text.x = element_text(angle = 45, hjust = 1),
            legend.position = "bottom",
            legend.title = element_text(size = 10),
            legend.text = element_text(size = 9),
            plot.margin = margin(20, 20, 20, 20)
          ) +
          scale_x_date(date_labels = "%Y-%m-%d", date_breaks = "1 week") +
          guides(color = guide_legend(nrow = 2, byrow = TRUE))
        
        # Show both plots at full width
        print(p_timeline)
        print(p_timeline_age)
        
        # Provide interpretation
        cat("\n📊 Timeline Analysis:\n")
        age_recruitment_summary <- weekly_by_age %>%
          group_by(adaptive_age_group) %>%
          summarise(
            total_responses = sum(n),
            weeks_active = n_distinct(week),
            avg_per_week = round(mean(n), 1),
            .groups = "drop"
          ) %>%
          arrange(desc(total_responses))
        
        cat("Age group recruitment patterns:\n")
        for (i in 1:nrow(age_recruitment_summary)) {
          cat(paste("  •", age_recruitment_summary$adaptive_age_group[i], ":", 
                    age_recruitment_summary$total_responses[i], "responses over",
                    age_recruitment_summary$weeks_active[i], "weeks\n"))
        }
        
      } else {
        print(p_timeline)
        cat("\n⚠️ Could not create age-stratified timeline - no age data linked to responses\n")
      }
    } else {
      print(p_timeline)
      cat("\n📊 Overall timeline shown - no age data available for stratification\n")
    }
  }
} else {
  cat("ℹ️ No date information found for timeline analysis.\n")
}
```

# 🔧 Data Quality Assessment

## Consent Status

```{r consent-analysis}
if (!is.null(responses_file) && "consent_ruling" %in% names(responses_file)) {
  consent_summary <- responses_file %>%
    filter(response_is_preview == FALSE) %>%
    count(consent_ruling) %>%
    mutate(percentage = round(n / sum(n) * 100, 1))
  
  # Consent status chart - full width
  plot_ly(consent_summary, 
          labels = ~consent_ruling, 
          values = ~n,
          type = 'pie',
          textposition = 'inside',
          textinfo = 'label+percent',
          marker = list(colors = c("#4CAF50", "#F44336", "#FF9800")),
          hovertemplate = "%{label}<br>Count: %{value}<br>Percentage: %{percent}<extra></extra>",
          width = 1000, height = 500) %>%
    layout(title = list(text = "Consent Status Distribution<br><sub>Essential for ethical compliance</sub>"),
           margin = list(l = 50, r = 50, t = 100, b = 50))
  
  cat("\n📊 Consent Analysis:\n")
  for (i in 1:nrow(consent_summary)) {
    cat(paste("  •", consent_summary$consent_ruling[i], ":", 
              consent_summary$n[i], "(", consent_summary$percentage[i], "%)\n"))
  }
}
```

## Eligibility Overview

```{r eligibility-analysis}
if (!is.null(responses_file) && any(str_detect(names(responses_file), "eligibility"))) {
  # Check eligibility columns
  eligible_responses <- responses_file %>%
    filter(response_is_preview == FALSE) %>%
    summarise(
      total = n(),
      eligible = sum(str_detect(response_eligibility_0 %||% "", "Eligible"), na.rm = TRUE),
      too_young = sum(str_detect(response_eligibility_0 %||% "", "TooYoung"), na.rm = TRUE),
      too_old = sum(str_detect(response_eligibility_0 %||% "", "TooOld"), na.rm = TRUE),
      other_ineligible = total - eligible - too_young - too_old
    )
  
  eligibility_data <- tibble(
    Status = c("Eligible", "Too Young", "Too Old", "Other Ineligible"),
    Count = c(eligible_responses$eligible, 
              eligible_responses$too_young,
              eligible_responses$too_old,
              eligible_responses$other_ineligible)
  ) %>%
    filter(Count > 0) %>%
    mutate(Percentage = round(Count / sum(Count) * 100, 1))
  
  if (nrow(eligibility_data) > 0) {
    plot_ly(eligibility_data, 
            x = ~Status, 
            y = ~Count, 
            type = 'bar',
            marker = list(color = colors[1:nrow(eligibility_data)]),
            text = ~paste("Count:", Count, "<br>Percentage:", Percentage, "%"),
            hovertemplate = "%{x}<br>%{text}<extra></extra>",
            width = 1000, height = 500) %>%
      layout(title = "Participant Eligibility Status",
             xaxis = list(title = "Eligibility Status"),
             yaxis = list(title = "Number of Responses"),
             margin = list(l = 50, r = 50, t = 100, b = 50))
  }
}
```

## Video Privacy Preferences

```{r video-privacy}
if (!is.null(responses_file) && "response_video_privacy" %in% names(responses_file)) {
  privacy_summary <- responses_file %>%
    filter(!is.na(response_video_privacy) & response_video_privacy != "") %>%
    count(response_video_privacy) %>%
    mutate(
      percentage = round(n / sum(n) * 100, 1),
      privacy_label = case_when(
        response_video_privacy == "private" ~ "Private (IRB only)",
        response_video_privacy == "scientific" ~ "Scientific/Educational", 
        response_video_privacy == "public" ~ "Public sharing allowed",
        response_video_privacy == "None" ~ "None specified",
        TRUE ~ as.character(response_video_privacy)
      )
    )
  
  # Create pie chart - full width
  plot_ly(privacy_summary, 
          labels = ~privacy_label, 
          values = ~n,
          type = 'pie',
          textposition = 'inside',
          textinfo = 'label+percent',
          marker = list(colors = colors[1:nrow(privacy_summary)]),
          hovertemplate = "%{label}<br>Count: %{value}<br>Percentage: %{percent}<extra></extra>",
          width = 1000, height = 500) %>%
    layout(title = list(text = "Video Privacy Preferences<br><sub>How parents want their videos to be used</sub>"),
           showlegend = TRUE,
           margin = list(l = 50, r = 50, t = 100, b = 50))
           
} else {
  cat("ℹ️ No video privacy column found in overview files.\n")
}
```

## Birthdate Verification

```{r birthdate-differences}
if (!is.null(responses_file) && "response_birthdate_difference" %in% names(responses_file)) {
  # Find rows with non-zero, non-blank birthdate differences
  birthdate_issues <- responses_file %>%
    filter(
      !is.na(response_birthdate_difference) & 
      response_birthdate_difference != 0 & 
      response_birthdate_difference != "" &
      response_birthdate_difference != "None"
    ) %>%
    select(
      child_hashed_id,
      response_uuid,
      response_birthdate_difference
    ) %>%
    arrange(desc(abs(as.numeric(response_birthdate_difference))))
  
  if (nrow(birthdate_issues) > 0) {
    # Create interactive table
    datatable(birthdate_issues,
              options = list(
                pageLength = 15,
                scrollX = TRUE,
                dom = 'Bfrtip',
                buttons = c('copy', 'csv', 'excel')
              ),
              filter = 'top',
              caption = "Birthdate Discrepancies Found",
              colnames = c(
                "Child Hashed ID" = "child_hashed_id",
                "Response UUID" = "response_uuid", 
                "Birthdate Difference (days)" = "response_birthdate_difference"
              )) %>%
      formatStyle(
        "Birthdate Difference (days)",
        backgroundColor = styleInterval(c(-30, 30), c("#ffcdd2", "#fff3e0", "#ffcdd2")),
        fontWeight = "bold"
      )
  } else {
    cat("✅ No birthdate discrepancies found.\n")
  }
} else {
  cat("ℹ️ No birthdate difference column found in overview files.\n")
}
```

## Parent Feedback

```{r parent-feedback}
if (!is.null(responses_file) && "response_parent_feedback" %in% names(responses_file)) {
  # Find rows with parent feedback (excluding "None" and blank values)
  parent_feedback_data <- responses_file %>%
    filter(
      !is.na(response_parent_feedback) & 
      response_parent_feedback != "" &
      response_parent_feedback != "None"
    ) %>%
    select(
      response_uuid,
      child_hashed_id,
      response_parent_feedback
    ) %>%
    arrange(response_uuid)
  
  if (nrow(parent_feedback_data) > 0) {
    # Create interactive table
    datatable(parent_feedback_data,
              options = list(
                pageLength = 15,
                scrollX = TRUE,
                dom = 'Bfrtip',
                buttons = c('copy', 'csv', 'excel')
              ),
              filter = 'top',
              caption = "Parent Feedback Responses",
              colnames = c(
                "Response UUID" = "response_uuid",
                "Child Hashed ID" = "child_hashed_id", 
                "Parent Feedback" = "response_parent_feedback"
              )) %>%
      formatStyle(
        "Parent Feedback",
        backgroundColor = "#e8f5e8",
        fontWeight = "bold"
      )
    
  } else {
    cat("ℹ️ No parent feedback found (all responses were 'None' or blank).\n")
  }
} else {
  cat("ℹ️ No parent feedback column found in overview files.\n")
}
```

# 💰 Payment Status Analysis

## Payment Overview

```{r payment-analysis}
if (!is.null(responses_file) && "response_researcher_payment_status" %in% names(responses_file)) {
  # Calculate payment statistics
  payment_summary <- responses_file %>%
    filter(response_is_preview == FALSE) %>%
    mutate(
      payment_status_clean = case_when(
        is.na(response_researcher_payment_status) ~ "Blank",
        response_researcher_payment_status == "" ~ "Blank", 
        response_researcher_payment_status == "To pay" ~ "To pay",
        TRUE ~ as.character(response_researcher_payment_status)
      )
    ) %>%
    count(payment_status_clean) %>%
    mutate(percentage = round(n / sum(n) * 100, 1))
  
  # Display summary statistics
  cat("📊 Payment Status Summary:\n")
  for (i in 1:nrow(payment_summary)) {
    cat(paste("  •", payment_summary$payment_status_clean[i], ":", 
              payment_summary$n[i], "(", payment_summary$percentage[i], "%)\n"))
  }
  
  total_responses <- sum(payment_summary$n)
  to_pay_count <- payment_summary$n[payment_summary$payment_status_clean == "To pay"]
  to_pay_count <- if(length(to_pay_count) > 0) to_pay_count else 0
  blank_count <- payment_summary$n[payment_summary$payment_status_clean == "Blank"]
  blank_count <- if(length(blank_count) > 0) blank_count else 0
  
  cat(paste("\n💡 Payment Insights:\n"))
  cat(paste("  • Total responses analyzed:", total_responses, "\n"))
  cat(paste("  • Participants awaiting payment:", to_pay_count, "\n"))
  cat(paste("  • Responses with no payment status:", blank_count, "\n"))
  
  if (to_pay_count > 0) {
    cat(paste("  • Outstanding payment rate:", round(to_pay_count / total_responses * 100, 1), "%\n"))
  }
  
} else {
  cat("ℹ️ No response_researcher_payment_status column found in overview files.\n")
}
```

## Payment Details Table

```{r payment-details-table}
if (!is.null(responses_file) && "response_researcher_payment_status" %in% names(responses_file)) {
  # Filter for "To pay" and blank responses
  payment_details <- responses_file %>%
    filter(
      response_is_preview == FALSE,
      (response_researcher_payment_status == "To pay" | 
       is.na(response_researcher_payment_status) | 
       response_researcher_payment_status == "")
    ) %>%
    mutate(
      payment_status_display = case_when(
        response_researcher_payment_status == "To pay" ~ "To pay",
        is.na(response_researcher_payment_status) ~ "Blank",
        response_researcher_payment_status == "" ~ "Blank",
        TRUE ~ as.character(response_researcher_payment_status)
      )
    ) %>%
    count(response_uuid, child_hashed_id, payment_status_display) %>%
    arrange(
      factor(payment_status_display, levels = c("To pay", "Blank")), 
      response_uuid
    )
  
  if (nrow(payment_details) > 0) {
    # Create interactive table
    datatable(payment_details,
              options = list(
                pageLength = 15,
                scrollX = TRUE,
                dom = 'Bfrtip',
                buttons = c('copy', 'csv', 'excel')
              ),
              filter = 'top',
              caption = "Payment Status Details - Unpaid and Blank Responses",
              colnames = c(
                "Response UUID" = "response_uuid",
                "Child Hashed ID" = "child_hashed_id", 
                "Payment Status" = "payment_status_display",
                "Count" = "n"
              )) %>%
      formatStyle(
        "Payment Status",
        backgroundColor = styleEqual(c("To pay", "Blank"), c("#fff3e0", "#ffebee")),
        fontWeight = "bold"
      )
  } else {
    cat("✅ All responses have been processed for payment.\n")
  }
} else {
  cat("ℹ️ No response_researcher_payment_status column found for detailed analysis.\n")
}
```

# 📁 Export Summary Data

```{r export-summary}
# Create analysis summary directory
analysis_dir <- file.path(paths$root, "analysis")
dir.create(analysis_dir, showWarnings = FALSE, recursive = TRUE)

# Export summary statistics
if (!is.null(responses_file)) {
  summary_export <- responses_file %>%
    filter(response_is_preview == FALSE) %>%
    select(
      response_id = response_id,
      response_uuid = response_uuid,
      child_hashed_id = child_hashed_id,
      participant_hashed_id = participant_hashed_id,
      date_created = response_date_created,
      completed = response_completed,
      withdrawn = response_withdrawn,
      consent_ruling = consent_ruling,
      any_of(c("child_age_rounded", "child_gender", "child_language_list"))
    )
  
  export_file <- file.path(analysis_dir, paste0("study_summary_", Sys.Date(), ".csv"))
  write_csv(summary_export, export_file)
  
  cat("✅ Summary data exported to:", export_file, "\n")
  cat("📁 Analysis directory:", analysis_dir, "\n")
}
```

# 📖 Summary & Next Steps

## Key Findings

```{r key-findings, results='asis'}
if (!is.null(responses_file)) {
  cat("### Study Overview\n\n")
  cat(paste("- **Total Participants:**", n_distinct(responses_file$child_hashed_id), "children\n"))
  cat(paste("- **Total Responses:**", nrow(responses_file %>% filter(response_is_preview == FALSE)), "sessions\n"))
  
  if ("response_completed" %in% names(responses_file)) {
    completion_rate <- round(mean(responses_file$response_completed == TRUE, na.rm = TRUE) * 100, 1)
    cat(paste("- **Completion Rate:**", completion_rate, "%\n"))
  }
  
  if (!is.null(age_processed) && nrow(age_processed) > 0) {
    cat(paste("- **Age Range:**", 
              round(min(age_processed$age_months, na.rm = TRUE)/12, 1), "-", 
              round(max(age_processed$age_months, na.rm = TRUE)/12, 1), "years\n"))
  }
  
  
}
```

---

*Generated with the Psych-DS Overview Analysis Template*  
*Report generated on `r Sys.Date()`*  
*Template focuses on participant demographics and study overview*
